---
title: "water-center_test"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r set abstract file & author objects, results = 'asis'}
meld <- read.csv("./TheAbstractSubmissions2018.csv")

first_author_name <- paste(meld$a, meld$b,sep = "")
MI = meld$MI; for(i in MI){
  if(is.na(MI[i]) == ""){
  }  else(MI == MI[i])
}
MI = gsub("[[:punct:]]", "", MI)#remove any '.' or other punctuation
author_name = stringr::str_to_title(paste(meld$a, MI, meld$b))#standardize the capitalization

first_coauthor = meld[,c( "g", "h")];second_coauthor = meld[,c("j", "k")]; third_coauthor = meld[, c("m", "n")];fourth_coauthor = meld[,c("p", "q")]; fifth_coauthor = meld[,c("s", "t")];sixth_coauthor= meld[,c("v", "w")]

coauthors = meld[,c("g", "h","j", "k","m", "n","p", "q","s", "t","v", "w")];coauthors$x = ""
title = meld[,'title']

for (i in 1:nrow(meld)){
print(as.character(droplevels(title[i])), size = 20)
  #for(j in 1:dim(coauthors)[2]){
    
  
 

  #print(paste(first_coauthor[i],",", second_coauthor[i],",",third_coauthor[i],",",fou)
  
}
```


```{r author, echo = F, results='asis'}

names = list()
for (i in 1:length(author_name)){
 z = min(which(apply(coauthors[i,], MARGIN = 2, ragtop::is.blank)))
 
names[i] = coauthors[i,1:as.numeric(z)];return(as.data.frame(unlist(names)))
  }
 #print(paste(author_name[i]), as.character(z)),size = 16)
```


```{r abstract, echo = F, results = 'asis'}
abstract = meld[,'abstract']

cat("\n\\newpage\n")
```

\documentclass[a4paper]{article}
%\usepackage{simplemargins}

%\usepackage[square]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\begin{document}
\pagenumbering{gobble}

\Large
 \begin{center}
Simple Single Page Abstract template\\ 

\hspace{10pt}

% Author names and affiliations
\large
Arthur Author$^1$, Cecilia CoAuthor$^2$ \\

\hspace{10pt}

\small  
$^1$) First affiliation\\
arthur.author@correspondence.email.com\\
$^2$) Second affiliation

\end{center}

\hspace{10pt}

\normalsize


\end{document}